Toward GPU-accelerated Traffic Simulation and Its Real-Time Challenge

### 2012-09-16 draft.tex
minor fixes

Computational workload is not the only issue of concern.
Deployment of traffic simulation may also require real-time feedback
from the real world, which turns out to be a cyber-physical systems
(CPS) problem indeed.
Real-time traffic simulation is another challenging issue, where
the rate and the preciseness of simulation must be traded to meet the
requirement of a given scenario.
For instance, simulation of emergent evacuation may want very high-rate
computation, even sacrificing preciseness of simulation to some extent.
Unfortunately, none of those challenges has been explored yet, largely
due to a lack of multidisciplinary collaborations between computationsl
physics and computer science.

@@

We consider that the problem of this scheme may be relevant to the
Imprecise Computation model~\cite{Lin1987}.
The Sample-in-CPU scheme is precise-but-slow, while the Sample-in-GPU
scheme is imprecise-but-fast.
If we are allowed to employ multiple GPUs in the system, we may run the
two types of simulation programs on different GPUs concurrently.
At some point of time $t$, the simulation result produced by the
Sample-in-GPU scheme represents a scenario way ahead of that produced by
the Sample-in-CPU scheme; the question is how precise it is.
Figure~\ref{fig:eval_error} demonstrates that the error in the
simulation result produced by the Sample-in-GPU scheme is getting larger
as time goes by.
If we can find such a time duration that causes the value of error to
fall out the acceptable range for practical use, we define this time
duration to be $\Delta t$.
Suppose that the two simulation programs based on the Sample-in-GPU and
the Sample-in-CPU schemes, respectively, are running concurrently.
At every interval of time $\Delta t$, we reset the simulation result
produced by the Sample-in-GPU scheme, and input the latest precise
simulation result produced by the Sample-in-CPU scheme during the same
interval.
By this means, the value of error in the simulation result produced by
the Sample-in-GPU scheme never falls out the acceptable range, while we
still benefit from its simulation speed within an internal of time
$\Delta t$.
The value of $\Delta t$ can be determined adaptively based on the
Imprecise Computation model.

@@

In future work, we extend our scheme to multidimensional OV models.
This extention allows our research to be applied to a broader range of
problems beyond freeways traffic simulation.
We also plan to consider a specific approach to the integration of the
Imprecise Computation model into our scheme in order to facilitate
deployment of traffic simulation in the real world.
Another interesting direction in this line of work is to coordinate with
engineering-based simulation such as AutoMatrix~\cite{Mangharam2011}.

>>>>

Computational workload is not the only issue of concern.
Deployment of traffic simulation may also require real-time feedback
from the real world, which turns out to be a cyber-physical systems
(CPS) problem indeed.
Real-time traffic simulation is another challenging issue, where
the rate and the preciseness of simulation must be traded to meet the
requirement of a given scenario.
For instance, simulation of emergent evacuation may want very high-rate
computation, even sacrificing preciseness of simulation to some extent.
Unfortunately, none of those challenges has been explored yet, largely
due to a lack of multidisciplinary collaborations between computational
physics and computer science.

@@

We consider that the problem of this scheme may be relevant to the
Imprecise Computation model~\cite{Lin1987}.
The Sample-in-CPU scheme is precise-but-slow, while the Sample-in-GPU
scheme is imprecise-but-fast.
If we are allowed to employ multiple GPUs in the system, we may run the
two types of simulation programs on different GPUs concurrently.
At some point of time $t$, the simulation result produced by the
Sample-in-GPU scheme represents a scenario way ahead of that produced by
the Sample-in-CPU scheme; the question is how precise it is.
Figure~\ref{fig:eval_error} demonstrates that the error in the
simulation result produced by the Sample-in-GPU scheme is getting larger
as time goes by.
If we can find such a time duration that causes the value of error to
fall out the acceptable range for practical use, we define this time
duration to be $\Delta t$.
Suppose that the two simulation programs based on the Sample-in-GPU and
the Sample-in-CPU schemes, respectively, are running concurrently.
At every interval of time $\Delta t$, we reset the simulation result
produced by the Sample-in-GPU scheme, and input the latest precise
simulation result produced by the Sample-in-CPU scheme during the same
interval.
By this means, the value of error in the simulation result produced by
the Sample-in-GPU scheme never falls out the acceptable range, while we
still benefit from its simulation speed within an internal of time
$\Delta t$.
The value of $\Delta t$ can be determined dynamically based on the
Imprecise Computation model.

@@

In future work, we extend our scheme to multidimensional OV models.
This extension allows our research to be applied to a broader range of
problems beyond freeways traffic simulation.
We also plan to consider a specific approach to the integration of the
Imprecise Computation model into our scheme in order to facilitate
deployment of traffic simulation in the real world.
Another interesting direction in this line of work is to coordinate with
engineering-based simulation such as AutoMatrix~\cite{Mangharam2011}.
